---
title: "Micro-ID Report"
format: 
  dashboard:
    embed-resources: false
    nav-buttons: [github]
    github: https://github.com/mine-cetinkaya-rundel/ld-dashboard
logo: images/logo.png
theme: [sandstone, theme/custom.scss]
fig-width: 10
fig-asp: 0.3
params:
  month: "June"
  year: "2024"
  us_cesarean_rate: 0.321 
  us_preterm_rate:  0.1049
  threshold_diff: 0.02
editor_options: 
  chunk_output_type: console
---

```{r, load packages}
#| label: load-packages
#| message: false

library(tidyverse)
library(readxl)
library(scales)
library(DT)
library(gt)
library(phyloseq)
#library(knitr)
#library(rcartocolor)
#library(microViz)
#library(vegan)
#library(broom)
#library(ggtext)
#library(plyr)
#library(DESeq2)
#library(plotly)
#library(modelsummary)
#library(MicrobiomeStat)
#library(microbiome)
#library(aplot)


theme_set(theme_minimal(base_size = 24, base_family = "Atkinson Hyperlegible"))
```

```{r, load data}
#| label: load-data
#| message: false

ps<- readRDS("data/ps_object.rds")


```

```{r, set inputs}}
#| label: set-inputs

time_period <- paste(params$month, params$year)
```

```{r, data prep}
#| label: prep-data


```

```{r, key fuctions}
#| label: key fuctions

#color picker
get_color <- function(value) {
  # Ensure the value is within the expected range
  if (value < 1 || value > 5) {
    stop("Value must be between 1 and 5")
  }
  
  # Define the color scale from red to yellow to blue
  color_palette <- colorRampPalette(c("#C21D00", "#FF932B", "#4655DF"))
  
  # Generate the colors for values 1 to 5
  colors <- color_palette(5)
  
  # Return the color corresponding to the input value
  return(colors[value])
}





```

#  {.sidebar}

Este panel muestra estadísticas para:

|             |                   |
|-------------|-------------------|
| **Cliente** | Salmones Spa      |
| **Unidad**  | Puerto Varas #1   |
| **Tipo Informe**  | Feed & Health   |
| **Month**   | `{r} time_period` |

------------------------------------------------------------------------

In `{r} time_period` the staff breakdown in the unit was as follows:

|                    |     |
|--------------------|-----|
| **Total Muestras** | 30  |
| **Controles**      | 15  |
| **Tratadas**       | 15  |

------------------------------------------------------------------------

::: {.callout-note collapse="true"}
## Disclaimer

Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500
:::

# Resumen

```{r, Resumen}
#| label: all-values
#| results: hide

num_species <- ntaxa(ps)


```

## Row {height="20%"}

```{r, value box Micro-ID Score}
#| content: valuebox
#| title: "Micro-ID Score"

list(
  icon = "moisture",
  color = get_color(1),
  value = num_species
)
``` 

```{r,  value box Scoring Salud}
#| content: valuebox
#| title: "Score Salud"

list(
  icon = "bug",
  color = get_color(2),
  value = num_species
)
```

```{r,  value boxScore Ecologia}
#| content: valuebox
#| title: Score Ecologia

list(
  icon = "clipboard2-pulse",
  color = get_color(3),
  value = num_species
)
```

```{r,  value boxScore Metabolico}
#| content: valuebox
#| title: "Score Metabolico"

list(
  icon = "bar-chart-steps",
  color = get_color(5),
  value = num_species
)
```

## Row {height="40%"}

### Column {width="60%"}

```{r, Distribucion Top Bacterias}
#| title: Distribucion Top Bacterias

plot(mtcars)

```

### Column {width="40%"}

```{r}
#| title: Grafico 2

plot(mtcars)

```

## Row {height="40%"}

Principales Conclusiones : Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.


# Salud {orientation="columns"}
## Column {width="60%"}

```{r, Valores Salud}
#| label: Ecology-values
#| results: hide

num_samples <- nsamples(ps)
```

### Row {height="20%"}

```{r, Value box 1}
#| component: valuebox
#| title: "box 1"

list(
  icon = "file-medical",
  color = "primary",
  value = num_samples
)
```

```{r, Value box 2}
#| component: valuebox
#| title: "box 2"

list(
  icon = "calendar-week",
  color = "primary",
  value = num_samples
)
```

```{r, Value box 3}
#| component: valuebox
#| title: "box 3"

list(
  icon = "calendar-week",
  color = "primary",
  value = num_samples
)
```
### Row {height="40%"}

```{r, Grafico Principal}
#| title: Grafico Principal

plot(mtcars)
```

#### Column {height="40%"}

En la primera sección de tu informe, verás 3 métricas diferentes para que comprendas la presencia total de bacterias en el cultivo de salmones. 

Total de bacterias beneficiosas (género): cantidad total de copias encontradas de bacterias beneficiosas.

Total de bacterias disruptivas (género): Cantidad total de copias encontradas de bacterias disruptivas. 

Proporción Beneficiosas/Disruptivas: Esta proporción establece la relación entre bacterias beneficiosas y disruptivas en tu muestra. Mayor cantidad de bacterias beneficiosas indica que el sistema se encuentra con un balance beneficioso, sin embargo, valores altos de bacterias disruptivas y perjudiciales indican que el sistema podría presentar una disbiosis. 


### Row {.tabset height="40%"}

```{r, Grafico 1}
#| title: Grafico 1

plot_bar(ps)
```

```{r Grafico2}
#| title: Grafico 2

plot_bar(ps)

```




